---
title: "Prevalence"
runtime: shiny
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```


```{r}
rm(list = ls())

#install.packages('survey')
#install.packages('dplyr')
library(survey)
library(ggplot2)
library(dplyr)

#Set working directory
setwd("/Users/changzhoug/GA Tech/Practicum/Prevalence")
#Read Data
q2b_1 = read.csv("q2_cancer.csv", head = TRUE, sep = ",")
```



```{r}
#Remove the unncessary columns
q2b <- subset(q2b_1, select = -c(X) )
#Defining Survey Weight
nhanes <- svydesign(id=~SDMVPSU, strata =~SDMVSTRA, weights=~DRX18YR, nest=TRUE, data =q2b)
```

```{r}
colnames(q2b)
c_cols <- c("X_id","HUQ010","HUQ050","HID010_2.0","SMD410_2.0", "HUQ020_2.0","HUQ020_3.0", "HUQ030_2.0","HUQ030_3.0","HUQ070_2.0","DMDBORN4_2.0","DMDCITZN_2.0","RIAGENDR_2.0","RIDRETH1_2.0","RIDRETH1_3.0","RIDRETH1_4.0", "RIDRETH1_5.0", "Year", "MCQ220", "ALQ101_2.0", "SMQ680_2.0", "BPQ020_2.0", "BPXPULS_2.0","PAQ635_2.0","PAQ650_2.0","PAQ665_2.0")
o_cols <- c("DMDHHSIZ","DMDHREDU", "INDFMINC")
q2b[c_cols] <- lapply(q2b[c_cols], factor)
q2b[o_cols] <- lapply(q2b[o_cols], ordered)
sapply(q2b, class)
```


# Calculating the Prevalence of Risk Factor for Cancer:

## Factor 1: DMDHHSIZ – Number of people in the household – 1 to 7 or more people
```{r}
# figure out the levels
levels <- svytable( ~ interaction(MCQ220, DMDHHSIZ) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(MCQ220, DMDHHSIZ))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
a <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```



```{r}
mat <- data.frame(a)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Cancer Prevalence
b <- mat[seq(2, nrow(mat), 2),]

#Get names of factors
b$Cond <- levels(factor(q2b$DMDHHSIZ))
```


Error Bar Plot:
```{r}
p <- ggplot(b, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Household Size (1 to 7+)",y= "Cancer Prevalence by Household Size", title="Cancer Prevalence by Household Size",fill = "Household Size", caption="source: CDC/NHANES") +
scale_y_continuous(breaks = pretty(b$Mean, n = 10)) 
#+ theme(axis.text.x = element_text(angle = 15, hjust = 1))

p +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
p +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```


## Factor 2: RIDRETH1_3.0 – Non-Hispanic White (1-yes, 0 – no)
```{r}
# figure out the levels
levels <- svytable( ~ interaction(MCQ220, RIDRETH1_3.0) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(MCQ220, RIDRETH1_3.0))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
c <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```



```{r}
mat <- data.frame(c)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Cancer Prevalence
d <- mat[seq(2, nrow(mat), 2),]

#Get names of factors
d$Cond <- levels(factor(q2b$RIDRETH1_3.0))
```


Error Bar Plot:
```{r}
q <- ggplot(d, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Non-Hispanic White (1-Yes, 0–No)",y= "Cancer by Non-Hispanic White", title="Cancer Prevalence in Non-Hispanic White", fill = "Non-Hispanic White (1-Yes, 0–No)", caption="source: CDC/NHANES") +
scale_y_continuous(breaks = pretty(d$Mean, n = 10)) 
#+ theme(axis.text.x = element_text(angle = 45, hjust = 1))

q +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
q +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```


## Factor 3: RIDAGEYR - Age at Screening
```{r}
# figure out the levels
levels <- svytable( ~ interaction(MCQ220, RIDAGEYR) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(MCQ220, RIDAGEYR))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
e <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```



```{r}
mat <- data.frame(e)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Cancer Prevalence
f <- mat[seq(2, nrow(mat), 2),]

#Get names of factors
f$AgeGroup <- levels(factor(q2b$RIDAGEYR))
```


Error Bar Plot:
```{r}
r <- ggplot(f, aes(x=AgeGroup, y=Mean, fill = AgeGroup)) + labs(x="Age Group",y= "Cancer by Age Group", title="Cancer Prevalence by Age Group", caption="source: CDC/NHANES") +
scale_y_continuous(breaks = pretty(f$Mean, n = 10))

r +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
r +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```


## Factor 4: RIAGENDR_2.0 – Female or Male (1 – female)
```{r}
# figure out the levels
levels <- svytable( ~ interaction(MCQ220, RIAGENDR_2.0) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(MCQ220, RIAGENDR_2.0))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
g <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```



```{r}
mat <- data.frame(g)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Cancer Prevalence
h <- mat[seq(2, nrow(mat), 2),]

#Get names of factors
h$Cond <- levels(factor(q2b$RIAGENDR_2.0))
```


Error Bar Plot:
```{r}
s <- ggplot(h, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Gender (0 - Male, 1 - Female)",y= "Cancer Prevalence by Gender", title="Cancer Prevalence by Gender",fill = "(0 - Male, 1 - Female)", caption="source: CDC/NHANES")

s +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
s +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```

## Factor 5: BPQ020_2.0 - Ever told you had high blood pressure (0-Yes, 1-No)
```{r}
# figure out the levels
levels <- svytable( ~ interaction(MCQ220, BPQ020_2.0) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(MCQ220, BPQ020_2.0))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
i <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```



```{r}
mat <- data.frame(i)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Cancer Prevalence
j <- mat[seq(2, nrow(mat), 2),]

#Get names of factors
j$Cond <- levels(factor(q2b$BPQ020_2.0))
```


Error Bar Plot:
```{r}
t <- ggplot(j, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Ever told you had High Blood Pressure (0-Yes, 1-No)",y= "Cancer by High Blood Pressure", title="Cancer Prevalence by High Blood Pressure",fill = "High Blood Pressure (0-Yes, 1-No)", caption="source: CDC/NHANES") 
t +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
t +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```

## Factor 6: HID010_2.0 – Covered by health insurance (0–Yes, 1–No)
```{r}
# figure out the levels
levels <- svytable( ~ interaction(MCQ220, HID010_2.0) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(MCQ220, HID010_2.0))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
o <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```



```{r}
mat <- data.frame(o)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Cancer Prevalence
p <- mat[seq(2, nrow(mat), 2),]

#Get names of factors
p$Cond <- levels(factor(q2b$HID010_2.0))
```


Error Bar Plot:
```{r}
q <- ggplot(p, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Covered by health insurance (0–Yes, 1–No)",y= "Cancer Prevalence by High Health Insurance", title="Cancer Prevalence by Health Insurance",fill = "Covered by health insurance (0–Yes, 1–No)", caption="source: CDC/NHANES") 
q +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
q +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```

## Overtime
```{r}
# figure out the levels
levels <- svytable( ~ interaction(MCQ220, Year) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(MCQ220, Year))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
k <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```



```{r}
mat <- data.frame(k)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Cancer Prevalence
l <- mat[seq(2, nrow(mat), 2),]

#Get names of factors
l$Cond <- c("1999-2000","2001-2002","2003-2004","2005-2006","2007-2008","2009-2010","2011-2012", "2013-2014", "2015-2016")
```


Error Bar Plot:
```{r}
u <- ggplot(l, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Years (1999-2016)",y= "Cancer", title="Cancer Over Time",fill = "Years", caption="source: CDC/NHANES") +
theme(axis.text.x = element_text(angle = 15, hjust = 1))
u +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
u +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```



## Overtime - Hospital Utilization
```{r}
# figure out the levels
levels <- svytable( ~ interaction(HUQ050, Year) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(HUQ050, Year))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
m <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```



```{r}
mat <- data.frame(m)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Hospital Utilization Disease Prevalence
n <- mat[seq(1, nrow(mat), 2),]

#Get names of factors
n$Cond <- c("1999-2000","2001-2002","2003-2004","2005-2006","2007-2008","2009-2010","2011-2012", "2013-2014", "2015-2016")
```


Error Bar Plot:
```{r}
v <- ggplot(n, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Years (1999-2016)",y= "Hospital Utilization", title="Hospital Utilization Over Time",fill = "Years", caption="source: CDC/NHANES") +
theme(axis.text.x = element_text(angle = 15, hjust = 1))
v +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
v +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```

## Overtime - Social Factors
```{r}
# figure out the levels
levels <- svytable( ~ interaction(DMDHREDU, Year) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(DMDHREDU, Year))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
a_1 <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```



```{r}
mat <- data.frame(a_1)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Socio Economic Factor Overtime Disease Prevalence
a_2 <- mat[seq(2, nrow(mat), 5),]

#Get names of factors
a_2$Cond <- c("1999-2000","2001-2002","2003-2004","2005-2006","2007-2008","2009-2010","2011-2012", "2013-2014", "2015-2016")

w <- ggplot(a_2, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Years (1999-2016)",y= "Proportion", title="Proportion of Education Levels Over Time",fill = "Education (Higher is more educated)", caption="source: CDC/NHANES") +
theme(axis.text.x = element_text(angle = 15, hjust = 1))
w +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
w +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```




## Overtime - Social Factors - Income
```{r}
# figure out the levels
levels <- svytable( ~ interaction(INDFMINC, Year) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(INDFMINC, Year))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
b_1 <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```



```{r}
mat <- data.frame(b_1)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Socio Economic Factor Overtime Disease Prevalence
b_2 <- mat[seq(8, nrow(mat), 11),]

#Get names of factors
b_2$Cond <- c("1999-2000","2001-2002","2003-2004","2005-2006","2007-2008","2009-2010","2011-2012", "2013-2014", "2015-2016")


x <- ggplot(b_2, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Years (1999-2016)",y= "Proportion", title="Proportion of Income Levels Over Time",fill = "Income", caption="source: CDC/NHANES") +
theme(axis.text.x = element_text(angle = 15, hjust = 1))
x +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
x +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```


## Overtime - Social Factors - Access to Healthcare
```{r}
# figure out the levels
levels <- svytable( ~ interaction(HUQ030_2.0, Year) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(HUQ030_2.0, Year))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
b_1 <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```



```{r}
mat <- data.frame(b_1)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Socio Economic Factor Overtime Disease Prevalence
b_2 <- mat[seq(2, nrow(mat), 2),]

#Get names of factors
b_2$Cond <- c("1999-2000","2001-2002","2003-2004","2005-2006","2007-2008","2009-2010","2011-2012", "2013-2014", "2015-2016")

## ERROR BAR PLOT ##
x <- ggplot(b_2, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Years (1999-2016)",y= "Proportion with No Access to Healthcare", title="Proportion of No Healthcare Access Over Time", caption="source: CDC/NHANES") +
theme(axis.text.x = element_text(angle = 15, hjust = 1)) + scale_fill_discrete(name = "No Healthcare Access")
x +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
x +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```


