---
title: "Q1 - Hospital Utilization Prevalence"
runtime: shiny
output: html_document
---

```{r}
#install.packages('survey')
#install.packages('dplyr')
library(survey)
library(ggplot2)
library(dplyr)
```


```{r}
rm(list = ls())

##############################
#Set working directory
setwd("/set/path")
##############################


```

```{r}
#Read Data
q1 = read.csv("Q1.csv", head = TRUE, sep = ",")
```


```{r}
#Remove the unncessary columns
q1 <- subset(q1, select = -c(X) )
#Defining Survey Weight
nhanes <- svydesign(id=~SDMVPSU, strata =~SDMVSTRA, weights=~DRX18YR, nest=TRUE, data =q1)
```

```{r}
colnames(q1)
c_cols <- c("X_id","HUQ010","HUQ050","HID010_2.0","SMD410_2.0","DIQ010_2.0","DIQ010_3.0","MCQ010_2.0", "HUQ020_2.0","HUQ020_3.0",   "HUQ030_2.0","HUQ030_3.0","HUQ070_2.0","DMDBORN4_2.0","DMDCITZN_2.0","RIAGENDR_2.0","RIDRETH1_2.0","RIDRETH1_3.0","RIDRETH1_4.0", "RIDRETH1_5.0", "Year")
o_cols <- c("DMDHHSIZ","DMDHREDU", "INDFMINC")
q1[c_cols] <- lapply(q1[c_cols], factor)
q1[o_cols] <- lapply(q1[o_cols], ordered)
sapply(q1, class)
```


# Calculating the Prevalence of Risk Factor for Hospital Utilization:

## Factor 1: HUQ030_2.0– Routine place to go for healthcare (2- there is no place)
```{r}
# figure out the levels
levels <- svytable( ~ interaction(HUQ050, HUQ030_2.0) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(HUQ050, HUQ030_2.0))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
a <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```



```{r}
mat <- data.frame(a)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Hospital Utilization Prevalence
b <- mat[seq(1, nrow(mat), 2),]

#Get names of factors
b$Cond <- levels(factor(q1$HUQ030_2.0))
```


Error Bar Plot:
```{r}
p <- ggplot(b, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Routine Place to go for Healthcare (0 - Yes, 1 - No)",y= "Hospital Utilization by Routine Place to go for Healthcare", title="Hospital Utilization Prevalence by Routine Place to go for Healthcare",fill = "(0 - Yes, 1 - No)", caption="source: CDC/NHANES") +
scale_y_continuous(breaks = pretty(b$Mean, n = 10))

p +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
p +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```


## Factor 2: HID010_2.0 – Covered by health insurance (Yes or No)
```{r}
# figure out the levels
levels <- svytable( ~ interaction(HUQ050, HID010_2.0) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(HUQ050, HID010_2.0))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
c <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```



```{r}
mat <- data.frame(c)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Hospital Utilization Prevalence
d <- mat[seq(1, nrow(mat), 2),]

#Get names of factors
d$Cond <- levels(factor(q1$HID010_2.0))
```


Error Bar Plot:
```{r}
q <- ggplot(d, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Covered by health insurance (Yes or No)",y= "Hospital Utilization by Health Insurance Coverage", title="Hospital Utilization Prevalence by Health Insurance Coverage",fill = "(0 - Yes, 1 - No)", caption="source: CDC/NHANES") +
scale_y_continuous(breaks = pretty(d$Mean, n = 10))

q +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
q +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```


## Factor 3: RIDAGEYR - Age at Screening
```{r}
# figure out the levels
levels <- svytable( ~ interaction(HUQ050, RIDAGEYR) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(HUQ050, RIDAGEYR))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
e <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```



```{r}
mat <- data.frame(e)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Hospital Utilization Prevalence
f <- mat[seq(1, nrow(mat), 2),]

#Get names of factors
f$AgeGroup <- levels(factor(q1$RIDAGEYR))
```


Error Bar Plot:
```{r}
r <- ggplot(f, aes(x=AgeGroup, y=Mean, fill = AgeGroup)) + labs(x="Age Group",y= "Hospital Utilization by Age Group", title="Hospital Utilization Prevalence by Age Group", caption="source: CDC/NHANES") 
#+ scale_y_continuous(breaks = pretty(f$Mean, n = 10))

r +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
r +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```


## Factor 4: RIAGENDR_2.0 – Female or Male (1 – female)
```{r}
# figure out the levels
levels <- svytable( ~ interaction(HUQ050, RIAGENDR_2.0) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(HUQ050, RIAGENDR_2.0))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
g <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```



```{r}
mat <- data.frame(g)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Hospital Utilization Prevalence
h <- mat[seq(1, nrow(mat), 2),]

#Get names of factors
h$Cond <- levels(factor(q1$RIAGENDR_2.0))
```


Error Bar Plot:
```{r}
s <- ggplot(h, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Gender (0 - Male, 1 - Female)",y= "Hospital Utilization by Gender", title="Hospital Utilization by Gender",fill = "(0 - Male, 1 - Female)", caption="source: CDC/NHANES")

s +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
s +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```

## Factor 5: DMDCITZN_2.0 – Not a citizen of the U.S. (1 – Not a citizen)
```{r}
# figure out the levels
levels <- svytable( ~ interaction(HUQ050, DMDCITZN_2.0) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(HUQ050, DMDCITZN_2.0))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
i <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```



```{r}
mat <- data.frame(i)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Hospital Utilization Prevalence
j <- mat[seq(1, nrow(mat), 2),]

#Get names of factors
j$Cond <- levels(factor(q1$DMDCITZN_2.0))
```


Error Bar Plot:
```{r}
t <- ggplot(j, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Citizen of the U.S (0 - Yes or 1 - No)",y= "Hospital Utilization by U.S. Citizenship", title="Hospital Utilization Prevalence by U.S. Citizenship",fill = "Citizen of U.S. (0 - Yes, 1 - No)", caption="source: CDC/NHANES") 
t +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
t +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```



## Overtime
```{r}
# figure out the levels
levels <- svytable( ~ interaction(HUQ050, Year) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(HUQ050, Year))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
k <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```



```{r}
mat <- data.frame(k)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Hospital Utilization Prevalence
l <- mat[seq(1, nrow(mat), 2),]

#Get names of factors
l$Cond <- c("1999-2000","2001-2002","2003-2004","2005-2006","2007-2008","2009-2010","2011-2012", "2013-2014", "2015-2016")
```


Error Bar Plot:
```{r}
u <- ggplot(l, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Years (1999-2016)",y= "Hospital Utilization", title="Hospital Utilization Over Time",fill = "Years", caption="source: CDC/NHANES") +
theme(axis.text.x = element_text(angle = 15, hjust = 1))
u +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
u +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```




