---
title: "Prevalence"
runtime: shiny
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```


```{r}
rm(list = ls())

#install.packages('survey')
#install.packages('dplyr')
library(survey)
library(ggplot2)
library(dplyr)

#Set working directory
setwd("/Users/changzhoug/GA Tech/Practicum/Prevalence/Q2/4 - Diabetes")
#Read Data
q2d_1 = read.csv("q2_diabetes.csv", head = TRUE, sep = ",")
```



```{r}
#Remove the unncessary columns
q2d <- subset(q2d_1, select = -c(X) )
#Defining Survey Weight
nhanes <- svydesign(id=~SDMVPSU, strata =~SDMVSTRA, weights=~DRX18YR, nest=TRUE, data =q2d)
```

```{r}
colnames(q2d)
c_cols <- c("X_id","HUQ010","HUQ050","HID010_2.0","SMD410_2.0", "HUQ020_2.0","HUQ020_3.0", "HUQ030_2.0","HUQ030_3.0","HUQ070_2.0","DMDBORN4_2.0","DMDCITZN_2.0","RIAGENDR_2.0","RIDRETH1_2.0","RIDRETH1_3.0","RIDRETH1_4.0", "RIDRETH1_5.0", "Year", "ALQ101_2.0", "SMQ680_2.0", "BPQ020_2.0")
o_cols <- c("DMDHHSIZ","DMDHREDU", "INDFMINC")
q2d[c_cols] <- lapply(q2d[c_cols], factor)
q2d[o_cols] <- lapply(q2d[o_cols], ordered)
sapply(q2d, class)
```


# Calculating the Prevalence of Risk Factor for Diabetes:

## Factor 1: DMDHHSIZ – Number of people in the household – 1 to 7 or more people
```{r}
# figure out the levels
levels <- svytable( ~ interaction(DIQ010, DMDHHSIZ) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(DIQ010, DMDHHSIZ))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
a <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```



```{r}
mat <- data.frame(a)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Diabetes Prevalence
b <- mat[seq(2, nrow(mat), 2),]

#Get names of factors
b$Cond <- levels(factor(q2d$DMDHHSIZ))

## ERROR BAR PLOT ##
p <- ggplot(b, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Household Size (1 to 7+)",y= "Diabetes Prevalence by Household Size", title="Diabetes Prevalence by Household Size",fill = "Household Size", caption="source: CDC/NHANES") +
scale_y_continuous(breaks = pretty(b$Mean, n = 10)) 
#+ theme(axis.text.x = element_text(angle = 15, hjust = 1))

p +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
p +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)

```



## Factor 2: RIDRETH1_3.0 – Non-Hispanic White (1-yes, 0 – no)
```{r}
# figure out the levels
levels <- svytable( ~ interaction(DIQ010, RIDRETH1_3.0) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(DIQ010, RIDRETH1_3.0))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
c <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```

```{r}
mat <- data.frame(c)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Diabetes Prevalence
d <- mat[seq(2, nrow(mat), 2),]

#Get names of factors
d$Cond <- levels(factor(q2d$RIDRETH1_3.0))

## ERROR BAR PLOT ###
q <- ggplot(d, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Non-Hispanic White (1-Yes, 0–No)",y= "Diabetes by Non-Hispanic White", title="Diabetes Prevalence in Non-Hispanic White", fill = "Non-Hispanic White (1-Yes, 0–No)", caption="source: CDC/NHANES") +
scale_y_continuous(breaks = pretty(d$Mean, n = 10)) 
#+ theme(axis.text.x = element_text(angle = 45, hjust = 1))

q +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
q +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```

## Factor 3: RIDAGEYR - Age at Screening
```{r}
# figure out the levels
levels <- svytable( ~ interaction(DIQ010, RIDAGEYR) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(DIQ010, RIDAGEYR))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
e <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```



```{r}

mat <- data.frame(e)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Diabetes Prevalence
f <- mat[seq(2, nrow(mat), 2),]

#Get names of factors
f$AgeGroup <- levels(factor(q2d$RIDAGEYR))

## ERROR BAR PLOT ##
r <- ggplot(f, aes(x=AgeGroup, y=Mean, fill = AgeGroup)) + labs(x="Age Group",y= "Diabetes by Age Group", title="Diabetes Prevalence by Age Group", caption="source: CDC/NHANES") 
#+ scale_y_continuous(breaks = pretty(f$Mean, n = 10))

r +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
r +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```


## Factor 4: RIAGENDR_2.0 – Female or Male (1 – female)
```{r}
# figure out the levels
levels <- svytable( ~ interaction(DIQ010, RIAGENDR_2.0) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(DIQ010, RIAGENDR_2.0))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
g <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```


```{r}
mat <- data.frame(g)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Diabetes Prevalence
h <- mat[seq(2, nrow(mat), 2),]

#Get names of factors
h$Cond <- levels(factor(q2d$RIAGENDR_2.0))

## ERROR BAR PLOT ##
s <- ggplot(h, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Gender (0 - Male, 1 - Female)",y= "Diabetes Prevalence by Gender", title="Diabetes Prevalence by Gender",fill = "(0 - Male, 1 - Female)", caption="source: CDC/NHANES")

s +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
s +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```

## Factor 5: BPQ020_2.0 - Ever told you had high blood pressure (0-Yes, 1-No)
```{r}
# figure out the levels
levels <- svytable( ~ interaction(DIQ010, BPQ020_2.0) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(DIQ010, BPQ020_2.0))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
i <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```


```{r}
mat <- data.frame(i)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Diabetes Prevalence
j <- mat[seq(2, nrow(mat), 2),]

#Get names of factors
j$Cond <- levels(factor(q2d$BPQ020_2.0))

## ERROR BAR PLOT ##
t <- ggplot(j, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Ever told you had High Blood Pressure (0-Yes, 1-No)",y= "Diabetes Proportion by High Blood Pressure", title="Diabetes Prevalence by High Blood Pressure",fill = "High Blood Pressure (0-Yes, 1-No)", caption="source: CDC/NHANES") 
t +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
t +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```


## Factor 6: HID010_2.0 – Covered by health insurance (0–Yes, 1–No)
```{r}
# figure out the levels
levels <- svytable( ~ interaction(DIQ010, HID010_2.0) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(DIQ010, HID010_2.0))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
o <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```


```{r}
mat <- data.frame(o)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Diabetes Prevalence
p <- mat[seq(2, nrow(mat), 2),]

#Get names of factors
p$Cond <- levels(factor(q2d$HID010_2.0))

## ERROR BAR PLOT ##
q <- ggplot(p, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Covered by health insurance (0–Yes, 1–No)",y= "Diabetes Prevalence by High Health Insurance", title="Diabetes Prevalence by Health Insurance",fill = "Covered by health insurance (0–Yes, 1–No)", caption="source: CDC/NHANES") 
q +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
q +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```


## Factor 7: MCQ010_2.0 – Ever been told you have asthma (0-Yes, 1-No)
```{r}
# figure out the levels
levels <- svytable( ~ interaction(DIQ010, MCQ010_2.0) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(DIQ010, MCQ010_2.0))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
c_1 <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```


```{r}
mat <- data.frame(c_1)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Diabetes Prevalence
c_2 <- mat[seq(2, nrow(mat), 2),]

#Get names of factors
c_2$Cond <- levels(factor(q2d$MCQ010_2.0))

## ERROR BAR PLOT ##
c_3 <- ggplot(c_2, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Ever told you had Asthma (0-Yes, 1-No)",y= "Diabetes Proportion by Asthma", title="Diabetes Prevalence by Asthma",fill = "Asthma (0-Yes, 1-No)", caption="source: CDC/NHANES") 
c_3  +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
c_3  +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```


## Factor 8: SMD410_2.0 – Does anyone smoke in the home? (0-Yes, 1-No)
```{r}
# figure out the levels
levels <- svytable( ~ interaction(DIQ010, SMD410_2.0) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(DIQ010, SMD410_2.0))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
d_1 <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```


```{r}
mat <- data.frame(d_1)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Diabetes Prevalence
d_2 <- mat[seq(2, nrow(mat), 2),]

#Get names of factors
d_2$Cond <- levels(factor(q2d$SMD410_2.0))

## ERROR BAR PLOT ##
d_3 <- ggplot(d_2, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Does anyone smoke in the home? (0-Yes, 1-No)",y= "Diabetes Prorportion by Smoking in Household", title="Diabetes Prevalence by Smoking in Household",fill = "Smoke (0-Yes, 1-No)", caption="source: CDC/NHANES") 
d_3 +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
d_3 +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```

## Factor 9: DMDBORN4_2.0 – Country of birth (0-U.S., 1-Other)
```{r}
# figure out the levels
levels <- svytable( ~ interaction(DIQ010, DMDBORN4_2.0) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(DIQ010, DMDBORN4_2.0))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
e_1 <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```


```{r}
mat <- data.frame(e_1)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Diabetes Prevalence
e_2 <- mat[seq(2, nrow(mat), 2),]

#Get names of factors
e_2$Cond <- levels(factor(q2d$DMDBORN4_2.0))

## ERROR BAR PLOT ##
e_3 <- ggplot(e_2, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Country of birth (0-U.S., 1-Other)",y= "Diabetes proportion by Country of Birth", title="Diabetes Prevalence by Country of Birth",fill = "Country of birth (0-U.S., 1-Other)", caption="source: CDC/NHANES") 
e_3 +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
e_3 +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```



## Factor 10: LBXTC – Total cholesterol (mg/dL)
```{r}
# figure out the levels
levels <- svytable( ~ interaction(DIQ010, LBXTC) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(DIQ010, LBXTC))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
e_1 <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```



```{r}
mat <- data.frame(e_1)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Diabetes Prevalence
e_2 <- mat[seq(2, nrow(mat), 2),]

#Get names of factors
e_2$Cond <- levels(factor(q2d$LBXTC))

## ERROR BAR ##
e_3 <- ggplot(e_2, aes(x=factor(Cond, level=c('Desirable (<200 mg/dL)', 'Borderline High (201-239 mg/dL)', 'High (>240 mg/dL)')), y=Mean, fill = Cond)) + labs(x="Total Cholesterol Levels",y= "Diabetes Prevalence by Total Cholesterol Levels", title="Diabetes Prevalence by Total Cholesterol Levels",fill = "Levels", caption="source: CDC/NHANES") +
scale_y_continuous(breaks = pretty(e_2$Mean, n = 10)) + theme(axis.text.x = element_text(angle = 15, hjust = 1))

e_3 +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
e_3 +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```


## Factor 11: LBDLDL – LDL-cholesterol (mg/dL)
```{r}
# figure out the levels
levels <- svytable( ~ interaction(DIQ010, LBDLDL) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(DIQ010, LBDLDL))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
f_1 <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```



```{r}
mat <- data.frame(f_1)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Diabetes Prevalence
f_2 <- mat[seq(2, nrow(mat), 2),]

#Get names of factors
f_2$Cond <- levels(factor(q2d$LBDLDL))

## ERROR BAR ##
f_3 <- ggplot(f_2, aes(x=factor(Cond, level=c('Desirable (<100 mg/dL)', 'Acceptable (100-129 mg/dL)', 'Borderline High(130-159 mg/dL)','High (160-189 mg/dL)', 'Very High (>190 mg/dL)')), y=Mean, fill = Cond)) + labs(x="LDL - Cholesterol Levels",y= "Diabetes Proportion by LDL - Cholesterol Levels", title="Diabetes Prevalence LDL - Cholesterol Levels",fill = "Levels", caption="source: CDC/NHANES") +
scale_y_continuous(breaks = pretty(f_2$Mean, n = 10)) +
theme(axis.text.x = element_text(angle = 45, hjust = 1))

f_3 +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
f_3 +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```


## Factor 12: BMXBMI - BMI 
```{r}
# figure out the levels
levels <- svytable( ~ interaction(DIQ010, BMXBMI) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(DIQ010, BMXBMI))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
g_1 <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```



```{r}
mat <- data.frame(g_1)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Diabetes Prevalence
g_2 <- mat[seq(2, nrow(mat), 2),]

#Get names of factors
g_2$Cond <- levels(factor(q2d$BMXBMI))

## ERROR BAR PLOT ##
g_3 <- ggplot(g_2, aes(x=factor(Cond, level=c('Underweight (BMI<18.5)', 'Normal (18.5-24.9)', 'Overweight (25-29.9)','Obese(30<BMI)')), y=Mean, fill = Cond)) + labs(x="BMI",y= "Diabetes Proportion by BMI Levels", title="Diabetes Prevalence BMI Levels",fill = "BMI Levels", caption="source: CDC/NHANES") + 
scale_y_continuous(breaks = pretty(g_2$Mean, n = 5)) +
theme(axis.text.x = element_text(angle = 45, hjust = 1))

g_3 +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
g_3 +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```



## Overtime - Label
```{r}
# figure out the levels
levels <- svytable( ~ interaction(DIQ010, Year) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(DIQ010, Year))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
k <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```


```{r}
mat <- data.frame(k)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Diabetes Prevalence
l <- mat[seq(2, nrow(mat), 2),]

#Get names of factors
l$Cond <- c("1999-2000","2001-2002","2003-2004","2005-2006","2007-2008","2009-2010","2011-2012", "2013-2014", "2015-2016")

## ERROR BAR PLOT ##
u <- ggplot(l, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Years (1999-2016)",y= "Diabetes", title="Diabetes Over Time",fill = "Years", caption="source: CDC/NHANES") +
theme(axis.text.x = element_text(angle = 15, hjust = 1))
u +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
u +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```


## Overtime - Hospital Utilization
```{r}
# figure out the levels
levels <- svytable( ~ interaction(HUQ050, Year) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(HUQ050, Year))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
m <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```



```{r}
mat <- data.frame(m)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Hospital Utilization Disease Prevalence
n <- mat[seq(1, nrow(mat), 2),]

#Get names of factors
n$Cond <- c("1999-2000","2001-2002","2003-2004","2005-2006","2007-2008","2009-2010","2011-2012", "2013-2014", "2015-2016")

## ERROR BAR PLOT ##
v <- ggplot(n, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Years (1999-2016)",y= "Hospital Utilization", title="Hospital Utilization Over Time",fill = "Years", caption="source: CDC/NHANES") +
theme(axis.text.x = element_text(angle = 15, hjust = 1))
v +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
v +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)


```


## Overtime - Social Factors
```{r}
# figure out the levels
levels <- svytable( ~ interaction(DMDHREDU, Year) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(DMDHREDU, Year))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
a_1 <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```



```{r}
mat <- data.frame(a_1)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Socio Economic Factor Overtime Disease Prevalence
a_2 <- mat[seq(2, nrow(mat), 5),]

#Get names of factors
a_2$Cond <- c("1999-2000","2001-2002","2003-2004","2005-2006","2007-2008","2009-2010","2011-2012", "2013-2014", "2015-2016")

## ERROR BAR PLOT ##
w <- ggplot(a_2, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Years (1999-2016)",y= "Proportion", title="Proportion of Education Levels Over Time",fill = "Education (Higher is more educated)", caption="source: CDC/NHANES") +
theme(axis.text.x = element_text(angle = 15, hjust = 1))
w +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
w +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```


## Overtime - Social Factors - Income
```{r}
# figure out the levels
levels <- svytable( ~ interaction(INDFMINC, Year) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(INDFMINC, Year))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
b_1 <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```



```{r}
mat <- data.frame(b_1)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Socio Economic Factor Overtime Disease Prevalence
b_2 <- mat[seq(11, nrow(mat), 11),]

#Get names of factors
b_2$Cond <- c("1999-2000","2001-2002","2003-2004","2005-2006","2007-2008","2009-2010","2011-2012", "2013-2014", "2015-2016")

## ERROR BAR PLOT ##
x <- ggplot(b_2, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Years (1999-2016)",y= "Proportion", title="Proportion of Income Levels Over Time",fill = "Income", caption="source: CDC/NHANES") +
theme(axis.text.x = element_text(angle = 15, hjust = 1))
x +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
x +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```


## Overtime - Social Factors - Access to Healthcare
```{r}
# figure out the levels
levels <- svytable( ~ interaction(HUQ030_2.0, Year) , nhanes )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(HUQ030_2.0, Year))"))

        res <- svyciprop( this_formula , nhanes , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
b_1 <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```



```{r}
mat <- data.frame(b_1)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Socio Economic Factor Overtime Disease Prevalence
b_2 <- mat[seq(2, nrow(mat), 2),]

#Get names of factors
b_2$Cond <- c("1999-2000","2001-2002","2003-2004","2005-2006","2007-2008","2009-2010","2011-2012", "2013-2014", "2015-2016")

## ERROR BAR PLOT ##
x <- ggplot(b_2, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Years (1999-2016)",y= "Proportion with No Access to Healthcare", title="Proportion of No Healthcare Access Over Time", caption="source: CDC/NHANES") +
theme(axis.text.x = element_text(angle = 15, hjust = 1)) + scale_fill_discrete(name = "No Healthcare Access")
x +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
x +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```

# Question 5:
```{r}
#Remove the unncessary columns
q2d_2 <- data.frame(q2d_1)
#Undiagnosed Diabetes where BMI > 30
undiag <- q2d_2 %>% 
  mutate(Undiagnosed_Diabetes = if_else(q2d_2$DIQ010==0 & q2d_2$BMXBMI == 'Obese(30<BMI)', 'Undiagnosed', 'Not Undiagnosed'))
```

```{r}
table(undiag$Undiagnosed_Diabetes)
```


```{r}
#Defining Survey Weight
nhanes_1 <- svydesign(id=~SDMVPSU, strata =~SDMVSTRA, weights=~DRX18YR, nest=TRUE, data =undiag)
```

## Undiagnosed Diabetes Over Time: Characterized by BMI > 30
```{r}
# figure out the levels
levels <- svytable( ~ interaction(Undiagnosed_Diabetes, Year) , nhanes_1 )


# calculate svyciprop zero/one for each possible level
svyciprop_fun <-
    function( this_level , ci = FALSE , ... ){
        this_formula <- as.formula( paste0( "~as.factor( '" , this_level , "' == interaction(HUQ030_2.0, Year))"))

        res <- svyciprop( this_formula , nhanes_1 , ... )
        if( ci ) res <- confint( res )
        res
    }


# use the default method
b_1 <- cbind(
    do.call( rbind , lapply( names( levels ) , svyciprop_fun ) ) ,
    do.call( rbind , lapply( names( levels ) , svyciprop_fun , ci = TRUE ) )
)
```



```{r}
mat <- data.frame(b_1)
colnames(mat) <- c("Mean", "Lower", "Upper")
rownames(mat) <- c(names(levels))
#Get only 1 - Undiagnosed Diabetes Overtime Prevalence
b_2 <- mat[seq(2, nrow(mat), 2),]

#Get names of factors
b_2$Cond <- c("1999-2000","2001-2002","2003-2004","2005-2006","2007-2008","2009-2010","2011-2012", "2013-2014", "2015-2016")

## ERROR BAR PLOT ##
x <- ggplot(b_2, aes(x=Cond, y=Mean, fill = Cond)) + labs(x="Years (1999-2016)",y= "Proportion with Undiagnosed Diabetes", title="Proportion of Undiagnosed Diabetes Over Time", caption="source: CDC/NHANES") +
theme(axis.text.x = element_text(angle = 25, hjust = 1)) + scale_fill_discrete(name = "Undiagnosed Diabetes")
x +
 geom_col(position = "dodge") +
 geom_errorbar(aes(ymin = Lower, ymax = Upper), position = "dodge", width = 0.25)


dodge <- position_dodge(width=0.9)
x +
  geom_col(position = dodge) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = dodge, width = 0.25)
```

